Paper Visualizations

### 2022-05-20 eda/paper-graphics.Rmd
updated table1 to html

---
title: "Paper Visualizations"
author: "Amanda Konet"
date: "`r date()`"
output: pdf_document
---

@@

stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.  Total Number of Amicus Briefs by Amicus Type in the Supreme Court Abortion Cases", notes = "a. Legal cases can have more than one amicus type filed in a case (e.g., differing groups of feminist organizations can file more than one brief in a case).  Also, the same organizations file briefs in multiple cases.", header=FALSE, notes.align = 'c')
```

>>>>

---
title: "Paper Visualizations"
author: "Amanda Konet"
date: "`r date()`"
output:
  html_document:
    df_print: paged
---

@@

total <- c("Total", sum(author_table$`Reproductive Rights`), sum(author_table$`Antiabortion`))
author_table <- rbind(author_table, total)

stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.  Total Number of Amicus Briefs by Amicus Type in the Supreme Court Abortion Cases", notes = "a. Legal cases can have more than one amicus type filed in a case (e.g., differing groups of feminist organizations can file more than one brief in a case).  Also, the same organizations file briefs in multiple cases.", header=FALSE, type = 'html', notes.align = 'l')
```
